\mireval{}

### 2014-05-08 paper/paper.tex
Conclusion

% Add conclusion
% Fill in missing segmentation explanations 
% Switch chord footnote to ref

@@

% Community development is crucial
As seen in the case of evaluating chord estimation systems, it is our hope that an open-source, publicly refined implementation might help resolve independently performed evaluation in the future. 
Furthermore, the difficulty faced in attempting to match the MIREX chord evaluation precisely clearly demonstrates the need for transparency and community involvement in comparative evaluation.
%; and two, we are curious as to how reliability of independently reported results in the literature.

>>>>

% Switch chord footnote to ref

@@

The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
This underlines the need for transparency and community involvement in comparative evaluation.
The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
By encouraging MIR researchers to use the same easily understandable evaluation codebase, we can ensure that different systems are being compared fairly.

While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards may change over time and that new metrics may be proposed.
Towards this end, \mireval{} is hosted on Github\footnote{URL redacted}, which provides a straightforward way of proposing changes to the codebase using the Pull Request feature.
With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.
